When are Fuzzy Extractors Possible?

### 2014-10-03 trunk/info-bounds/FuzzyExtPossibility.tex
edited "techniques" in the intro

\paragraph{Techniques} In the distribution-aware setting, we construct a secure sketch for an arbitrary distribution $W$.  We begin with distributions where all points have roughly the same probability.  We call this type of distribution nearly flat.  Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must describe which point $w\in W$ within distance $t$ of $w'$ was sketched.  The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.   Thus, for nearly flat distributions, security is maintained if we always provide enough information to disambiguate the ball with the greatest number of points.  We use universal hashing to disambiguate points.

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call levels.  We then write down the level of the original reading $w$ and apply the above construction considering only points in that level.  We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.

Our negative results are in the distribution-oblivious setting.  A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).  However, $\gen$ does not see the distribution $W$, only the sample $w$.  This creates an asymmetry, the adversary knows $W$, while $\gen$ only knows the sample $w$ and the family of distributions $\mathcal{W}$.  We construct a family of distributions $\mathcal{W}$ where having seen $w$, the remainder of the support is uniform.  Our family $\mathcal{W}$ is the set of affine lines.  For any distribution, the nonsecret value $p$ partitions the metric space into regions that produce a consistent value under $\rep$.  For each of these regions, the adversary knows that possible $w$ lie far from the boundary of the region.  However, in the Hamming space the majority of points lie near the boundary.  Since the fuzzy extractor does not know the rest of $W$, it places most points of $W$ near a boundary.  This means that $W|p$ is small.  This is enough to break security.

@@

Fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}

>>>>

\paragraph{Techniques for Positive Results for Known Distributions} We now explain how to construct a secure sketch for an arbitrary known distribution $W$ (we already explained how to construct a fuzzy extractor from it).  We begin with distributions in which all points in the support have roughly the same probability.  We call distributions of this type ``nearly flat.''  Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must disambiguiate which point $w\in W$ within distance $t$ of $w'$ was sketched. Disambiguating multiple points can be accomplished by universal hashing, as long as the number of possible hash outputs is slightly greater than the number of possible points. Thus, our sketch is computed via a universal hash of $w$. To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$. Because the distribution is nearly flat, it is also the ball with the most points of nonzero probability. Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball. Since $\Hfuzz$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz$.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ''levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.  We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.

\paragraph{Techniques for Negative Results for Distribution Families}
Note constructing a family of distributions $\mathcal{W}$ and proving impossibility for a uniformly random (rather than worst-case) $W\in \mathcal{W}$  is sufficient.
We start by observing the following asymmetry: $\gen$  see only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
the adversary knows $W$.   To exploit the asymmetry, we construct $\mathcal{W}$ so that conditioning on the knowledge of $W$ reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on the entire space.

Then we show how the adversary can exploit the knowledge of the affine line to reduce the uncertainty about $w$ (in the secure sketch case) or $\key$ (in the fuzzy extractor case). 
In the secure sketch case, $\sketch$ can be used to find fixed points of $\rec(\cdot, \sketch)$ which, by the correctness requirement of the sketch, must be separated by minimum distance $t$. This means there aren't too many of them, so few can lie on an average line, permitting the adversary to guess one easily.

In the fuzzy extractor case, the nonsecret value $p$ partitions the metric space into regions that produce a consistent value under $\rep$ (preimages of each $\key$ under $\rep(\cdot, p)$).  For each of these regions, the adversary knows that possible $w$ lie $t$-far from the boundary of the region.  However, in the Hamming space, the vast majority of points lie near the boundary (this follows by combining the isoperimetric inequality~\cite{harper1966optimal} showing that the ball has the smallest boundary and Hoeffding's inequality~\cite{hoeffding1963probability} for bounding the volume that is $t$-away from this boundary).  This allows the adversary to rule out so many possible $w$ that, combined with the adversarial knowledge of the affine line, most regions become empty, leaving $\key$ far from uniform.

We note that the use of a high-dimensional Hamming space is important: fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}

\lnote{old two pars below this line --- do we need anything?}

We construct a family of distributions $\mathcal{W}$ for which knowing only a single value $w$ leaves the remainder of the support is uniform.  Our family $\mathcal{W}$ is the set of affine lines.  For any distribution, the nonsecret value $p$ partitions the metric space into regions that produce a consistent value under $\rep$.  For each of these regions, the adversary knows that possible $w$ lie far from the boundary of the region.  However, in the Hamming space the majority of points lie near the boundary.  Since the fuzzy extractor does not know the rest of $W$, it places most points of $W$ near a boundary.  This means that $W|p$ is small.  This is enough to break security.

@@
